WORCS: A Workflow for Open Reproducible Code in Science

### 2020-11-05 paper/Manuscript_DS.Rmd
Fix Aaron's affiliation

---
author:
  name: |
    [Caspar J. Van Lissa](c.j.vanlissa@uu.nl)$^{a,b}$
    Andreas M. Brandmaier$^{c,d}$
    Loek Brinkman$^{b,e}$
    Anna-Lena Lamprecht$^{b,f}$
    Aaron Peikert$^{c,g}$
    Marijn E. Struiksma$^{b,h}$
    Barbara Vreede$^{i}$

  affiliation: | 
      a: Utrecht University faculty of Social and Behavioral Sciences, department of Methodology & Statistics  
      b: Open Science Community Utrecht  
      c: Center for Lifespan Psychology, Max Planck Institute for Human Development, Berlin, Germany  
      d: Max Planck UCL Centre for Computational Psychiatry and Ageing Research, Berlin, Germany and London, UK  
      e: UMC Utrecht  
      f: Utrecht University, Department of Information and Computing Sciences  
      g: Humboldt-Universitaet zu Berlin  
      h: Utrecht University faculty of Humanities, department of Language, Literature & Communication, Utrecht Institute of Linguistics OTS  
      i: University Library Utrecht
title: "WORCS: A Workflow for Open Reproducible Code in Science"
short:      "WORKFLOW FOR OPEN SCIENCE"
shorttitle:      "WORKFLOW FOR OPEN SCIENCE"
abstract: |
  Adopting open science
  principles can be challenging and time-intensive, because doing so requires
  substantial conceptual education and training in the use of new tools.
  This paper introduces the Workflow for
  Open Reproducible Code in Science (WORCS): A step-by-step
  procedure that researchers can follow to make a research project open and
  reproducible.
  The purpose of the workflow is to lower the threshold for 
  adoption of open science principles.
  It is based on best practices, and can be used either in
  parallel to, or in absence of, top-down requirements by journals,
  institutions, and funding bodies.
  To facilitate widespread adoption, the WORCS principles have been implemented
  in the R package `worcs`, which offers an RStudio 
  project template and utility functions for specific workflow steps.
  This paper introduces the conceptual workflow,
  discusses how it meets different 
  standards for open science, and provides examples of the implementation in `R`. 
  This paper is primarily targeted towards
  scholars conducting research projects in R on a private computer,
  conducting research that involves academic prose, analysis code,
  and (optionally) tabular data.
  However, the workflow is flexible enough to accommodate other scenarios,
  and offers a sensible starting point for customized solutions.
  The source code for the `R` package and manuscript,
  and a list of user examples of WORCS projects, are available at 
  https://github.com/cjvanlissa/worcs.
authornote: "blabla"
keywords:
  # at least one keyword must be supplied
  formatted: [open science, reproducibility, r, dynamic document generation, version control]
  plain:     [open science, reproducibility, r, dynamic document generation, version control]
preamble: >
  \usepackage{amsmath}
bibliography      : ["worcs.bib"]  
urlcolor          : blue
output: rmarkdown::html_document
---
<!--
, "worcs_packages.bib"
output: 
  rmarkdown::html_document:
    citation_package: biblatex Note: Citations are always handled by pandoc when format is not PDF
knit: worcs::cite_all
csl: apa.csl
csl: apa.csl
-->

>>>>

---
author:
  name: |
    [Caspar J. Van Lissa](c.j.vanlissa@uu.nl)$^{a,b}$
    Andreas M. Brandmaier$^{c,d}$
    Loek Brinkman$^{b,e}$
    Anna-Lena Lamprecht$^{b,f}$
    Aaron Peikert$^{c}$
    Marijn E. Struiksma$^{b,g}$
    Barbara Vreede$^{h}$

  affiliation: | 
      a: Utrecht University faculty of Social and Behavioral Sciences, department of Methodology & Statistics  
      b: Open Science Community Utrecht  
      c: Center for Lifespan Psychology, Max Planck Institute for Human Development, Berlin, Germany  
      d: Max Planck UCL Centre for Computational Psychiatry and Ageing Research, Berlin, Germany and London, UK  
      e: UMC Utrecht  
      f: Utrecht University, Department of Information and Computing Sciences  
      g: Utrecht University faculty of Humanities, department of Language, Literature & Communication, Utrecht Institute of Linguistics OTS  
      h: University Library Utrecht
title: "WORCS: A Workflow for Open Reproducible Code in Science"
short:      "WORKFLOW FOR OPEN SCIENCE"
shorttitle:      "WORKFLOW FOR OPEN SCIENCE"
abstract: |
  Adopting open science
  principles can be challenging and time-intensive, because doing so requires
  substantial conceptual education and training in the use of new tools.
  This paper introduces the Workflow for
  Open Reproducible Code in Science (WORCS): A step-by-step
  procedure that researchers can follow to make a research project open and
  reproducible.
  The purpose of the workflow is to lower the threshold for 
  adoption of open science principles.
  It is based on best practices, and can be used either in
  parallel to, or in absence of, top-down requirements by journals,
  institutions, and funding bodies.
  To facilitate widespread adoption, the WORCS principles have been implemented
  in the R package `worcs`, which offers an RStudio 
  project template and utility functions for specific workflow steps.
  This paper introduces the conceptual workflow,
  discusses how it meets different 
  standards for open science, and provides examples of the implementation in `R`. 
  This paper is primarily targeted towards
  scholars conducting research projects in R on a private computer,
  conducting research that involves academic prose, analysis code,
  and (optionally) tabular data.
  However, the workflow is flexible enough to accommodate other scenarios,
  and offers a sensible starting point for customized solutions.
  The source code for the `R` package and manuscript,
  and a list of user examples of WORCS projects, are available at 
  https://github.com/cjvanlissa/worcs.
authornote: "blabla"
keywords:
  # at least one keyword must be supplied
  formatted: [open science, reproducibility, r, dynamic document generation, version control]
  plain:     [open science, reproducibility, r, dynamic document generation, version control]
preamble: >
  \usepackage{amsmath}
bibliography      : ["worcs.bib"]  
urlcolor          : blue
output: rmarkdown::html_document
---
<!--
, "worcs_packages.bib"
output: 
  rmarkdown::html_document:
    citation_package: biblatex Note: Citations are always handled by pandoc when format is not PDF
knit: worcs::cite_all
csl: apa.csl
csl: apa.csl
-->
